Применение жестов мышью в CASE-системах

### 2010-09-01 articles/mouseGestures/article.tex
fixed pictures' size to fit in table cell

\begin{center}
\begin{table} [ht]
  \label{experimentsTable}
  \fontsize{8}{11}
  \selectfont
  \begin{tabular} {| c | c | c | c | c | c | c | c |}
    \hline
    \multirow{2}{*}{Жест} & \multirow{2}{*}{Идеальный жест} & \multicolumn{2}{c}{Распознано} & \multicolumn{2}{|c}{Ложно-позитивных} & \multicolumn{2}{|c|}{Не распознано} \\
    \cline{3-8}
                          &                          & rect    & qt         & rect   & qt        & rect   & qt \\ \hline     
    1&   \includegraphics[scale=0.5]{gesture1.png}   & 26\%    & 11\%       & 74\%   & 1\%       & 0\%    & 88\% \\ \hline
    2&   \includegraphics[scale=0.5]{gesture2.png}   & 94\%    & 3\%        & 1\%    & 0\%       & 5\%    & 97\% \\ \hline
    3&   \includegraphics[scale=0.5]{gesture3.png}   & 92\%    & 100\%      & 1\%    & 0\%       & 7\%    & 0\% \\ \hline
    4&   \includegraphics[scale=0.5]{gesture4.png}   & 61\%    & 19\%       & 38\%   & 15\%      & 1\%    & 66\% \\ \hline
    5&   \includegraphics[scale=0.5]{gesture5.png}   & 98\%    & 57\%       & 2\%    & 0\%       & 0\%    & 43\% \\ \hline
    6&   \includegraphics[scale=0.5]{gesture6.png}   & 96\%    & 0\%        & 1\%    & 15\%      & 3\%    & 85\% \\ \hline
    7&   \includegraphics[scale=0.35]{gesture7.png}  & 69\%    & 95\%       & 30\%   & 0\%       & 1\%    & 5\% \\ \hline
    8&   \includegraphics[scale=0.5]{gesture8.png}   & 98\%    & 25\%       & 2\%    & 3\%       & 0\%    & 72\% \\ \hline
    9&   \includegraphics[scale=0.5]{gesture9.png}   & 84\%    & 92\%       & 0\%    & 0\%       & 16\%   & 8\% \\ \hline
    10&  \includegraphics[scale=0.5]{gesture10.png}  & 93\%    & 0\%        & 5\%    & 63\%      & 2\%    & 37\% \\ \hline
  \end{tabular}
  \caption{Результаты экспериментов}
\end{table}
\end{center}

>>>>

\begin{center}
\begin{table} [ht]
  \label{experimentsTable}
  \fontsize{8}{20}
  \selectfont
  \begin{tabular} {| c | c | c | c | c | c | c | c |}
    \hline
    \multirow{2}{*}{Жест} & \multirow{2}{*}{Идеальный жест} & \multicolumn{2}{c}{Распознано} & \multicolumn{2}{|c}{Ложно-позитивных} & \multicolumn{2}{|c|}{Не распознано} \\
    \cline{3-8}
                          &                          & rect    & qt         & rect   & qt        & rect   & qt \\ \hline     
    1&   \scalebox{0.5}{\includegraphics[scale=0.5]{gesture1.png}}   & 26\%    & 11\%       & 74\%   & 1\%       & 0\%    & 88\% \\ \hline
    2&   \scalebox{0.5}{\includegraphics[scale=0.5]{gesture2.png}}   & 94\%    & 3\%        & 1\%    & 0\%       & 5\%    & 97\% \\ \hline
    3&   \scalebox{0.5}{\includegraphics[scale=0.5]{gesture3.png}}   & 92\%    & 100\%      & 1\%    & 0\%       & 7\%    & 0\% \\ \hline
    4&   \scalebox{0.5}{\includegraphics[scale=0.5]{gesture4.png}}   & 61\%    & 19\%       & 38\%   & 15\%      & 1\%    & 66\% \\ \hline
    5&   \scalebox{0.5}{\includegraphics[scale=0.5]{gesture5.png}}   & 98\%    & 57\%       & 2\%    & 0\%       & 0\%    & 43\% \\ \hline
    6&   \scalebox{0.5}{\includegraphics[scale=0.5]{gesture6.png}}   & 96\%    & 0\%        & 1\%    & 15\%      & 3\%    & 85\% \\ \hline
    7&   \scalebox{0.45}{\includegraphics[scale=0.35]{gesture7.png}}  & 69\%    & 95\%       & 30\%   & 0\%       & 1\%    & 5\% \\ \hline
    8&   \scalebox{0.5}{\includegraphics[scale=0.5]{gesture8.png}}   & 98\%    & 25\%       & 2\%    & 3\%       & 0\%    & 72\% \\ \hline
    9&   \scalebox{0.5}{\includegraphics[scale=0.5]{gesture9.png}}   & 84\%    & 92\%       & 0\%    & 0\%       & 16\%   & 8\% \\ \hline
    10&  \scalebox{0.5}{\includegraphics[scale=0.5]{gesture10.png}}  & 93\%    & 0\%        & 5\%    & 63\%      & 2\%    & 37\% \\ \hline
  \end{tabular}
  \caption{Результаты сравнения алгоритмов}
\end{table}
\end{center}
